Extended Data

### 2022-03-12 doc/manuscript/Dow_manuscript_Nature.Rmd
methods work

Measurements were timed to begin before the beginning of spring growth and to continue through the cessation of growth in the fall. 
At SCBI, the median start date was April 14, which was adjusted forward when early leaf-out of understory vegetation was observed, with the earliest start date being March 30 (in 2020). 
Measurements were continued through to fall leaf senescence, with the median end date being October 17 and the latest end date November 26 (2012). 
*Timing of measurements at Harvard Forest were similar, with the median start date of April 23 and median end date of October 30.* <!--Does this change?-->
All measurements from 1998 were dropped because of a late start date (**DATE**).
*1999 was an anomalous year where initial measurements were taken on January 5, but not taken again until April 15.* <!--I think we dropped this.Correct?-->
The latest end date was November 11, 2002.
In our analysis, each band-year was treated independently, with no data overlap from one year to the next.

>>>>

Measurements were timed to begin before the beginning of spring growth and to continue through the cessation of growth in the fall. 
At SCBI, the median start date was April 14, which was adjusted forward when early leaf-out of understory vegetation was observed, with the earliest start date being March 30 (in 2020). 
Measurements were continued through to fall leaf senescence, with the median end date being October 17 and the latest end date November 26 (2012). 
*Timing of measurements at Harvard Forest were similar, with the median start date of April 23 and median end date of October 30.* <!--Changes depending on when we calculate median. I think we can calculate it before removal of 1998 since we technically incude 1998 in our raw data, just remove it during our data cleaning. If you don't like that, it cahges to: start: april 21, end: October 27-->
All measurements from 1998 were dropped because of a late start date (May 26).
*1999 was an anomalous year where initial measurements were taken on January 5, but not taken again until April 15.* <!--I think we dropped this.Correct? CD: No, left in. This could influence growth in 1999 if "a" was selected based on pre-hydration, winter DBH, but I have faith that Sean's process to find "a" can handle this. That being said, it is unfortunate that 1999 is the only year with early measurements and very weird timing. Justification for my faith: If "a" uses prehydration, winter dbh, then we would expect the "a" in 1999 to be proportionally smaller than in other years. This smaller "a" coupled with an unchanged "b" (last measurement was about the same in 1999 as other years) would result in greater total growth (b-a). But we actually see that 1999 total growth is the smallest, indicating to me that the hot summer is driving the weirdness. -->
The latest end date was November 11, 2002.
In our analysis, each band-year was treated independently, with no data overlap from one year to the next.
